Perturbation Theory in the Complex Plane: Exceptional Points and Where to Find Them

### 2020-11-30 Manuscript/EPAWTFT.tex
fixed my axisvi EPAWTFT.tex
changed notation to lambda_EP not lambda_c

%------------------------------------------------------------------%
% Figure on the UMP critical point
%------------------------------------------------------------------%
\begin{figure*}[t]
\begin{subfigure}{0.49\textwidth}
\includegraphics[height=0.65\textwidth]{ump_critical_point}
\subcaption{\label{subfig:ump_cp}}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
\includegraphics[height=0.65\textwidth]{ump_ep_to_cp}
\subcaption{\label{subfig:ump_ep_to_cp}}
\end{subfigure}
\caption{%
\hugh{%
    The UMP ground-state EP becomes a critical point in the strong correlation limit (large $U/t$).
    (\subref{subfig:ump_cp}) As the $U/t$ increases, the avoided crossing on the real $\lambda$ axis
    becomes increasingly sharp.
    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs onto the real axis for $U/t \rightarrow \infty$
    mirrors the formation of the RMP critical point and other QPTs in the infinite basis set limit.
}
\label{fig:UMP_cp}}

>>>>

%------------------------------------------------------------------%
% Figure on the UMP critical point
%------------------------------------------------------------------%
\begin{figure*}[t]
\begin{subfigure}{0.49\textwidth}
    \includegraphics[height=0.65\textwidth,trim={0pt 5pt 0pt 15pt}, clip]{ump_critical_point}
\subcaption{\label{subfig:ump_cp}}
\end{subfigure}
\begin{subfigure}{0.49\textwidth}
\includegraphics[height=0.65\textwidth]{ump_ep_to_cp}
\subcaption{\label{subfig:ump_ep_to_cp}}
\end{subfigure}
\caption{%
\hugh{%
    The UMP ground-state EP becomes a critical point in the strong correlation limit (large $U/t$).
    (\subref{subfig:ump_cp}) As the $U/t$ increases, the avoided crossing on the real $\lambda$ axis
    becomes increasingly sharp.
    (\subref{subfig:ump_ep_to_cp}) The convergence of the EPs at $\lep$ onto the real axis for $U/t \rightarrow \infty$
    mirrors the formation of the RMP critical point and other QPTs in the infinite basis set limit.
}
\label{fig:UMP_cp}}
